Self Regulation Ontology Retest Analyses

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
added clinical versus control sample analyses for the literature

>>>>

Are there differences between clinical and non-clinical samples in the literature?

```{r}
tmp = lit_review %>%
  mutate(clinical = as.character(clinical),
         clinical = ifelse(clinical == "", "control", clinical),
         clinical_1_0 = ifelse(clinical == "control", 0, 1))
table(tmp$clinical)
table(tmp$clinical_1_0)
summary(lmer(retest_reliability ~ clinical_1_0+(1|dv),data=tmp))
```
